### 2024-06-06 conteudo/01-exemplo-normas-ime.tex
Fix error

Given the complexity of Types 3 and 4 of code duplications, the state-of-art approches that aims at this type of
duplication constantly have a high cost in computational time and memory space \citep{letreview}, which is a concern in our research 
that aim to work in large codebases scopes. For this reason we will look after mainly at Type 1 and 2 of code duplications.

>>>>

Given the complexity of  types 3 and 4 of code duplications, the state-of-art approches that aims at this type of
duplication constantly have a high cost in computational time and memory space \citep{litreview}, which is a concern in our research 
that aim to work in large codebases scopes. For this reason we will look after mainly at type 1 and 2 of code duplications.
